Prefetching SPARQL query cacher

### 2016-05-26 dissertation/cache-proxy.tex
small

This procedure would allow the cost model to balance the cost between
doing a Cartesian join and doing a remote SPARQL evaluation of data
already in the cache.

>>>>

This procedure would allow the cost model to balance the cost between
doing a Cartesian join and doing a remote SPARQL evaluation of data
already in the cache, as plans for both these options would be provided.
